
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}
\usepackage{ragged2e}

\usepackage{xcolor}
\hypersetup{colorlinks,urlcolor=blue}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
\usepackage[sfdefault]{noto-sans}
%\usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
%\usepackage{charter}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor= MidnightBlue,
    pdftitle={Pranav's Resume},
    pdfpagemode=FullScreen,
    }
    
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\Large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\achievementItem}[1]{
  \item\normalsize{
    {#1 \vspace{-6pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\normalsize{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\normalsize #2} \\
      \textit{\normalsize#3} & \textit{\normalsize #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\normalsize#1} & \textit{\normalsize #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \normalsize#1 & \textbf{\normalsize #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify \begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Pranav Goel} \\ \vspace{1pt}
    % 123 Street Name, Town, State 12345 \\ 
    \vspace{5pt}
    \normalsize \raisebox{-0.1\height}\faPhone\ 9599091897 ~ 
    \raisebox{-0.2\height}\faEnvelope\ \href{mailto:pranavgoel2012@gmail.com}{ pranavgoel2012@gmail.com} ~ 
    \raisebox{-0.2\height}\faTwitter\ \href{https://www.twitter.com/iipranavii/}{ twitter.com/iipranavii}  ~
    \raisebox{-0.2\height}\faGithub\ \href{https://github.com/iipranavii}{ github.com/iipranavii}
    \vspace{-8pt}
\end{center}



\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {\href{https://compete.peakmind.in/}{PeakMind}}{Jan '22 -- Present}
      {UX Design Intern}{Remote}
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Analysed the Comeptitive Space of Education/ Self-Help Apps}
        \resumeItem{Created a User Journey for Pomodoro based app}
        \resumeItem{Worked on the User Flow as well as Design for a Assessment targetted towards the Adolescent and Young Adults}
        \resumeItem{Brainstormed on user accessability as well as resultant feedback on each step}
        \resumeItem{Designed the complete Assesment page as well as a Personalised Result page, including Wireframes, High Fidelity Designs and Prototypes}
      \resumeItemListEnd
      
    \resumeSubheading
      {\href{https://apihacks.devpost.com/}{API Hacks 2.0}}{July '21 -- Oct '21}
      {Organiser}{Remote}
      \vspace{-7pt}
      \resumeItemListStart
        \resumeItem{Designed the Hackathon Logo and Visual Components for Socials}
        \resumeItem{Engaged within the Community to Uplift Innovation and Ideation.}
        \resumeItem{Developed the Sponsor and Community Literature.}
        \resumeItem{Hosted Workshops with Speakers from various Domains.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {\href{https://github.com/imabp/getsponsors/}{\textbf{SponsorBlok}} $|$ \emph{StoryBloks, NextJS, AnimeJS, Figma}}{October 2021}
            \resumeItemListStart
                \resumeItem{\textbf{Created a Cohesive Platform for Organizers and Companies to Reach out and Avail Sponsorships.}}
                \resumeItem{Designed the Landing page and the Workflow of the Service.}
                \resumeItem{Developed a System to Reach out to multiple companies and keep track of available sponsorships in one place.}
            \resumeItemListEnd
        \resumeProjectHeading
            {\href{https://github.com/iipranavii/Feedback-Prime}{\textbf{Feedback Prime}} $|$ \emph{Symbl.ai, Kotlin, Sawo Labs, Figma}}{October 2021} 
            \resumeItemListStart
                \resumeItem{\textbf{Created an AI-based system to Intelligently understand a customer support call, and analyse the pain points during the conversation.}}
                \resumeItem{Developed a straightforward Interface to easily upload call recordings and get an instant analysis of each Dialogue.}
                \resumeItem{Designed a minimalistic UI for a clutter-free experience.}
            \resumeItemListEnd 
        \resumeProjectHeading
            {\href{https://github.com/iipranavii/Suite-Converter}{\textbf{Suite Converter}} $|$ \emph{Python, Speech Recognition, gTTS}}{January 2021} 
            \resumeItemListStart
                \resumeItem{\textbf{Created a CLi Program to Locally Inter-Convert Multiple Common File Types. }}
                \resumeItem{Devised a solution to convert Files without Internet Connection.}
                \resumeItem{Implemented gTTS Python library to convert User's Voice into Printable text file.}
            \resumeItemListEnd 
    \resumeSubHeadingListEnd


%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    {\item{
     \textbf{Languages}{:C++, Python, HTML, CSS, Javascript } \\
     \vspace{1pt}
     \textbf{Developer Tools}{: Git, GitHub, Vercel } \\
     \vspace{1pt}
     \textbf{Design Tools}{: Figma, Adobe XD, Illustrator, Photoshop, Webflow} \\
    }}
 \end{itemize}
 \vspace{-16pt}

   %-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Chandigarh University, Mohali}{September '20 -- August '24}
      {Bachelor of Technology in Computer Science - Cloud Computing}{Mohali, Punjab, India}
  \resumeSubHeadingListEnd


%-----------INVOLVEMENT---------------
\section{ACHIEVEMENTS \& EXTRA-CURRICULAR}

\begin{itemize}[leftmargin=0.2in]
  \achievementItem{\href{https://badgr.com/public/assertions/VVxNa822Quinhvm6DbWzoA}{\textbf{Postman Student Expert}}: a program designed to promote API literacy amongst students and educators.}
  \achievementItem{Won \textbf{1\textsuperscript{st}} Prize in \href{https://apiworld.co/hackathon}{API World Hackathon} for \textbf{Feedback Prime} in Symbl.ai Challenge - Go Beyond Speech Recognition with Conversation Intelligence APIs}
  \achievementItem{Won StoryBlok Track at \href{https://hackthisfall.tech/}{Hack this Fall Hackathon} for SponsorBlok for the Best Integration of Storyblok within our project. }
\end{itemize}
        
    % \resumeSubHeadingListEnd
\end{document}

%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
